Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-22 latex/ms.tex
add 4th para in Results section, #13

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}

@@

We numerically evaluated the performance of ${\hat M}$ or ${\hat m}$ for the case in which variable reproductive potential among parents. Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$. {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$). Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.

@@

As sample size or migrants increase, the precision increases and the shape of the distribution asymptotically becomes symmetric ({\bf Figure~\ref{violins}}). This is because increasing of a sample size or migrants increases of the probability that randomly selected two individuals share kinship between the two populations and thus decreases the CV.

@@

\subsection{Invasive sampling}

>>>>

@@

We numerically evaluated the performance of ${\hat M}$s or ${\hat m}$s for the case in which variable reproductive potential among parents. Scaled statistical properties of ${\hat m_1}$,  ${\hat m_2}$,  ${\hat m_3}$ and ${\hat m_4}$ are completely the same to ${\hat M_1}$, ${\hat M_2}$, ${\hat M_3}$ and ${\hat M_4}$, hereafter, we only demonstrate the results of ${\hat M_1}$-${\hat M_5}$. {\bf Figure~\ref{violins}} illustrates the distribution of the relative bias of ${\hat M}$ for limiting cases where parent and offspring sample numbers are identical (i.e., $n=n_{\rm P,1}=n_{\rm P,2}=n_{\rm O,1}= n_{\rm O,2}$) and parent numbers in the two populations are also identical (i.e., $N=N_1=N_2$). Relative bias is calculated by applying outputs of the individual-based model, which is defined as follows: ``averaged estimator - true value/true value.'' Full list of parameter sets to evaluate the performance (relative bias and CV of ${\hat M}$s) is summarized in {\bf Table S1} in {\bf Supporting Information}.

@@

As sample size or migrants increase, the precision increases and the shape of the distribution asymptotically becomes symmetric ({\bf Figure~\ref{violins}}). This is because an increasing of sample size or migrants is likely to increase the observed number of kinship pairs found between two populations ($\widetilde{H}_{\rm HS,bet}$ or $\widetilde{H}_{\rm PO,bet}$) and decreases the variance of those kinship pair numbers. In addition, the number of PO pair within a population ($\widetilde{H}_{\rm PO,1}$ or $\widetilde{H}_{\rm PO,2}$) also contributes the precision for estimating $N_1$ or $N_1$, respectively, providing ${\hat M_4}$ and ${\hat M_5}$ with a higher precision.

Our simulator can handle the situation with or without invasive sampling. Invasive sampling potentially affect the $m$ since sampled parents in the population 1 have no chance to move to the population 2 and thus those parents cannot be sampled. In this case, $m$ should be defined by $M/(N_1-n_{P,1})$ not by $M/N_1$, although it does not affect the estimator ${\hat M}$s, as demonstrated in {\bf Table S1} ({\bf Supporting Information}).

\RED{kokomade!!!!!!!!!!!!!!!!!!!!}
\subsection{Invasive sampling}

@@
